%! TEX program = lualatex
%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{minhuacv}

% For mathematical symbols
\usepackage{amsmath}
% character encoding
\usepackage[utf8]{inputenc}
\usepackage{CJKutf8}



% Set applicant's personal data for header
\name{Minhua Chen}
\address{PuDong \linebreak Shanghai China}
\contacts{(86) 15221358935 \linebreak chenmhgo@gmail.com}

\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Software Engineer}{BlackLake}{2016/11 - Now}
			\begin{itemize}
				\item Developed manufacturing execution system from stracth, designed and implemented core backend services.
				\item Developed data syncing service for syncing MySQL data into ElasticSearch automatically, which is the fundamental compoment of all searching service and tracing service.
				\item Improved data history tracing system by using adaptive data schema, reduced 80\% disk space and 30\% api latency.
				\item Developed file service with switchable storage services (AWS S3, QINIU and MinIO).
				\item Developed job scheduling service for making business intelligence data report.
				\item Developed customizable concurrency limiter library for protecting key OPEN HTTP API.
				\item Developed object tracking prototype with YOLOv3 and NVIDIA JETSON.
				\item Leaded backend team to migrate from NodeJS/ExpressJS to Kotlin/Spring.
				\item Leveragedskills:Java,Kotlin,NodeJS,ExpressJS,MySQL,ElasticSearch,Redis,Kafka,SpringBoot,Spring Cloud, Kubernetes, Tensorflow.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Engineer, Intern}{IBM CRL}{2015/7 - 2016/1}	
			\begin{itemize}
				\item Developed health care service prototype with multi-tenancy architecture from stracth (full stack).
				\item Utilized Echart to visualize biological data. Raspberry pi as sensor gateway; RabbitMQ as pub/sub channel.
				\item Developed event-driven engine by Node-RED for emergency alerting feature.
				\item Leveraged skills: Java, NodeJS, React, EChart, MySQL, RabbitMQ.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Teaching Assistant}{Shanghaitech University}{2015/2 - 2015/7}		
			\begin{itemize}
				\item Courses: Introduction to information Technology.
				\item Build a website for teaching students algorithms and data structure. https://suanfa.herokuapp.com/
			\end{itemize}
		\end{cvsubsection}
		
	\end{cvsection}
	
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Shanghai, China}{Shanghaitech University}{2014/8 -- 2017/5}
			\begin{itemize}
				\item M.S.E. in Information Science and Technology, May 2017. GPA: 3.5
				\item Course: Algorithms; Machine Learning; Computer Vision; Compressed Sensing; Matrix Analysis; Digital Signal Processing; Robotics; Entrepreneurship.
				\item Research Topic: Convolutional Recurrent Neural Network-based Channel Equalization.
				\item Reward: Thrid Prize in National Post-Graduate Mathematical Contest in Modeling
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{Nanjing, China}{Southeast University}{2010/8 -- 2014/6}
			\begin{itemize}
				\item B.S.E. in Information Science and Technology, June 2014. GPA: 3.6.
				\item Course: Digital Circuit; Analog Circuit; Communication Theory; Signals and Systems; Digital Signal Processing; Computer Organization And Architecture.
				\item Reward: Thrid Prize in National Undergraduate Electronics Design Contest.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Technical Experience}
		\begin{cvsubsection}{Side projects}{}{}
			\begin{itemize}
				\item \textbf{Website for Algorithms} (2015) https://suanfa.herokuapp.com/
				\item \textbf{Gituser - command line tool for github user profile} (2016) https://github.com/chenminhua/gituser 
				\item \textbf{RNGIT - A github mobile app} (2016) https://github.com/chenminhua/RNGIT
				\item \textbf{Pin - A clipboard on network} (2019) https://github.com/chenminhua/pin
				\item \textbf{Github} (2014 - Now) https://github.com/chenminhua
				\item \textbf{Personal Blog} (2015 - Now) https://chenminhua.github.io
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Skills}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item \textbf{Programming Language} Java; C; Python; JavaScript; Golang;
				\item \textbf{Web Framewark} Spring; Flask; ExpressJS;
				\item \textbf{Database} MySQL; Redis; 
				\item \textbf{Miscellaneous} Kafka; Elastic search; Git; Kubernetes; Docker;
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
\end{document}
